---
title: "Hurricanes Vignette"
author: "Swetha Garimalla"
date: "June 17, 2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



##Load Data

Load data from [RAMMB: The Tropical Cyclone Extended Best Track Dataset][via](http://rammb.cira.colostate.edu/research/tropical_cyclones/tc_extended_best_track_dataset/).

```{r, echo=FALSE, eval=FALSE}
raw.data <- load_data(filename = "ebtrk_atlc_1988_2015.txt") 
raw.data
```

## Clean Data

This is a function that takes the output of \code{load_data()} (above) in a 
tibble format, 
1) creates a new column called \code{storm_id} where \code{storm_name} 
and \code{year} are merged with a hyphen (ex: "KATRINA-2005"). 
2) A second column is also created, \code{date}, that reformats the month, day, year, and hour data from the original data to have one ymd_hms formatted column. 
3) The data is then gathered by the 4 directions x 3 windspeeds. 
4) The key of this is then separated to retrieve \code{windspeed}, \code{radius}, and \code{direction}. 
5) The \code{direction} is then spread into 4 columns, one for each direction. 
6) The \code{longitude} is mutated to be negative and account for the western hemisphere. 
7) Finally, specific columns are selected for the output tibble. This function returns a tibble that contains the columns \code{storm_id}, \code{date}, \code{latitude}, \code{longitude}, \code{wind_speed}, \code{ne}, \code{nw}, \code{se}, \code{sw}
```{r, echo=FALSE, eval=FALSE}
data <- load_data(filename = "ebtrk_atlc_1988_2015.txt") %>% clean_data()
data
```
## Select Data
This is a function that takes the output of \code{clean_data()} (above) in a  tibble format and filters by \code{storm_name} and \code{date} such that the output is specifically related to one date and time. 

```{r, echo=FALSE, eval=FALSE}
data <- load_data(filename = "ebtrk_atlc_1988_2015.txt") 
        %>% clean_data() %>% select_data()
data
```

## Create Hurricane Geom Plot
This is a function takes the output of \code{select_data} above and produces an image
which is three circles overlayed, each split into 4 quadrants. 

```{r, echo=FALSE, eval=FALSE}
map_data <- get_map("Louisiana", zoom = 6, maptype = "toner-background")
base_map <- ggmap(map_data, extent = "device")

base_map +
  geom_hurricane(data = hurricane, aes(x = longitude, y = latitude,
                                       r_ne = ne, r_se = se,
                                       r_nw = nw, r_sw = sw,
                                       fill = wind_speed,
                                       color = wind_speed))
```

